Why aren't significance tests commonly used for linear regression diagnostics?

### 2022-10-01 paper_comparison/paper_comparison/paper_comparison.Rmd
fill in exp overview

Graphical summaries in which residuals are plotted against fitted values or other functions of the predictor variables that are approximately orthogonal to residuals are referred to as standard residual plots in @cook1982residuals. As shown in Figure \ref{fig:residual-plot-common-departures}, the top-left panel is a good residual plot with residuals evenly distributed at both sides of the horizontal zero line showing no noticeable patterns. There are various types of departures from a good residual plot. Two most commonly checked departures - non-linearity, heterskedasticity and non-normality will be discussed in this paper.

Non-linearity is a type of model misspecification caused by failing to include higher order terms of the regressors in the regression equation. Any non-linear functional form of residuals on fitted values presented in the residual plot could be considered as an indicative of non-linearity. An example residual plot containing visual pattern of non-linearity is given at the top-right of Figure [ref here]. One can clearly observe the "S-shape" from the residual plot as the cubic term is not captured by the misspecified model.

Heterskedasticity refers to the presence of nonconst error variance in a regression model. It is mostly due to the strict but false assumptions on the variance-covariance matrix of the error term. The usual pattern of heterskedasticity on a residual plot is the inconsistent spread of the residuals at different x values. Visually, it sometimes results in the so-called "butterfly" shape as shown in the bottom-left panel of Figure \ref{fig:residual-plot-common-departures}, or the "left-triangle" and "right-triganle" shape where the smallest variance occurs at the edges of the x-axis.

Compared to non-linearity and heterskedasticity, non-normality is usually harder to be detected from a residual plot since scatter plot is not excel in revealing marginal distribution. A favourable graphical summarise for this task is the quantile-quantile plot. However, for a consistent comparison in the later part of this paper, residual plot will be the focus. Besides, it is important to note that not all regression models assume normality for the error term, but a certain amount do including the classical normal linear regression model. In the case that the normality assumption is violated, it is expected to observe data points that do not centralize around the horizontal zero line and unevenly distribute at both sides of the zero line. For example, given a skewed error distribution, fewer data points and more outliers are on one side of the zero line as shown at the bottom-right of Figure \ref{fig:residual-plot-common-departures}.

@@

As pointed out by @vanderplas2021statistical, the binomial model doesn't take into account the possible dependencies in the visual test due to repeated evaluations of the same lineup. And it is inapplicable to visual test where subjects are asked to select one or more "most different" plots from the lineup. They summarized three common scenarios in visual inference: (1) $K$ different lineups are shown to $K$ subjects, (2) $K$ lineups with different null plots but the same actual data plot are shown to $K$ subjects, and (3) the same lineup is shown to $K$ subjects. Out of these three scenarios, Scenario 3 is the most common in previous studies as it puts the least constraints on the experimental design. For Scenario 3, @vanderplas2021statistical modelled the probability of a plot $i$ being selected from a lineup as $\theta_i$, where $\theta_i \sim Dirichlet(\alpha)$ for $i=1,...,m$ and $\alpha > 0$. And defined $c_i$ to be the number of times plot $i$ being selected in $K$ evaluations. In case subject $j$ makes multiple selections, $1/s_j$ will be added to $c_i$ instead of one, where $s_j$ is the number of plots subject $j$ selected for $j=1,...K$. This ensured $\sum_{i}c_i=K$. Since we are only interested in the selections of the actual data plot $i$, the marginal model can be simplified to a beta-binomial model and thus the visual p-value is given as`

@@

```{=tex}
\begin{equation} \label{eq:pvalue-beta-binomial}
P(C \geq c_i) = \sum_{x=c_i}^{K}\frac{\Gamma(K + 1)}{\Gamma(x + 1)\Gamma(K - x + 1)}\frac{B(x + \alpha, K - x + (m - 1)\alpha)}{B(\alpha, (m-1)\alpha)}dx,
\end{equation}
```

@@

As discussed in @majumder_validation_2013, individual's skill will affect the number of observers who identify the actual data plot from the lineup. Thus, the power of a visual test depends on the subject-specific abilities. Previously, it was addressed by modelling the probability of a subject $i$ correctly picking the actual data plot from a lineup $l$ using a mixed-effect logistic regression with the subject being treated as a random effect [@majumder_validation_2013]. However, knowing this probability is insufficient to determine the power of a visual test allowed for multiple selections as it doesn't provide information about the number of selections made by the subject, and hence, the p-value can't be computed. Recall that the p-value is computed

(1) Instead, we modelled the probability of a lineup being rejected directly using a logistic regression with the natural logarithm of the effect size as the only regressor. The same model was applied to different subsets of the survey data for making comparison of the power.

(2) Instead, we modelled the plot selection $c_i$ for the actual data plot $i$.

<!-- -   Very briefly explain what a lineup test is -->

<!-- -   Lineup (maybe using your previous residual plot for nonlinearity) -->

<!-- -   $p$-value calulcation, briefly, including how multiple selections are handled -->

<!-- -   power calculation, briefly, including how multiple selections are handled -->

```{=html}
<!-- ![Parallelism between multiple quantitative testing and visual discovery [@buja_statistical_2009]. Visible features in a plot are viewed as a collection of test statistics $T^{(i)}(\boldsymbol{\mathrm{y}})~(i \in I)$, and any visual discoveries that are inconsistent with the null hypothesis are treated as evidence against the null. For regression diagnostics, the null hypothesis would be the assumed model, and visual discoveries could be any visual features in favour of any alternatives. \label{fig:parallelism}](figures/rsta2009012001.jpg){width=450 height=341}
-->
```

@@

Three experiments were conducted to investigate the difference between conventional hypothesis testing and graphical diagnostics in the application of linear regression diagnostics. The experiment I has ideal scenario for conventional testing, where the visual test is not expected to outperform the conventional test. The experiment II is a scenario where the conventional test is an approximate test, in which the visual test may have a chance to match the performance of the conventional test. The experiment III is designed for collecting human responses to lineup with only good residual plots such that the parameter $\alpha$ in Equation \ref{eq:pvalue-beta-binomial} can be estimated. Overall, we planned to collect 7974 evaluations on 1152 uniqued lineups performed by 443 subjects throughout three experiment.

@@

Two types of departures were considered with the corresponding data generating process being designed for experiment I and II.

>>>>

Graphical summaries in which residuals are plotted against fitted values or other functions of the predictor variables that are approximately orthogonal to residuals are referred to as standard residual plots in @cook1982residuals. As shown in Figure \ref{fig:residual-plot-common-departures}, the top-left panel is a good residual plot with residuals evenly distributed at both sides of the horizontal zero line showing no noticeable patterns. There are various types of departures from a good residual plot.

Non-linearity, heterskedasticity and non-normality are perhaps the three mostly commonly checked departures. Non-linearity is a type of model misspecification caused by failing to include higher order terms of the regressors in the regression equation. Any non-linear functional form of residuals on fitted values presented in the residual plot could be considered as an indicative of non-linearity. An example residual plot containing visual pattern of non-linearity is given at the top-right of Figure [ref here]. One can clearly observe the "S-shape" from the residual plot as the cubic term is not captured by the misspecified model. Heterskedasticity refers to the presence of nonconst error variance in a regression model. It is mostly due to the strict but false assumptions on the variance-covariance matrix of the error term. The usual pattern of heterskedasticity on a residual plot is the inconsistent spread of the residuals at different x values. Visually, it sometimes results in the so-called "butterfly" shape as shown in the bottom-left panel of Figure \ref{fig:residual-plot-common-departures}, or the "left-triangle" and "right-triganle" shape where the smallest variance occurs at the edges of the x-axis. Compared to non-linearity and heterskedasticity, non-normality is usually harder to be detected from a residual plot since scatter plot is not excel in revealing marginal distribution. A favourable graphical summarise for this task is the quantile-quantile plot. However, for a consistent comparison in the later part of this paper, residual plot will be the focus. Besides, it is important to note that not all regression models assume normality for the error term, but a certain amount do including the classical normal linear regression model. In the case that the normality assumption is violated, it is expected to observe data points that do not centralize around the horizontal zero line and unevenly distribute at both sides of the zero line. For example, given a skewed error distribution, fewer data points and more outliers are on one side of the zero line as shown at the bottom-right of Figure \ref{fig:residual-plot-common-departures}.

@@

As pointed out by @vanderplas2021statistical, the binomial model doesn't take into account the possible dependencies in the visual test due to repeated evaluations of the same lineup. And it is inapplicable to visual test where subjects are asked to select one or more "most different" plots from the lineup. They summarized three common scenarios in visual inference: (1) $K$ different lineups are shown to $K$ subjects, (2) $K$ lineups with different null plots but the same actual data plot are shown to $K$ subjects, and (3) the same lineup is shown to $K$ subjects. Out of these three scenarios, Scenario 3 is the most common in previous studies as it puts the least constraints on the experimental design. For Scenario 3, @vanderplas2021statistical modelled the probability of a plot $i$ being selected from a lineup as $\theta_i$, where $\theta_i \sim Dirichlet(\alpha)$ for $i=1,...,m$ and $\alpha > 0$. And defined $c_i$ to be the number of times plot $i$ being selected in $K$ evaluations. In case subject $j$ makes multiple selections, $1/s_j$ will be added to $c_i$ instead of one, where $s_j$ is the number of plots subject $j$ selected for $j=1,...K$. This ensured $\sum_{i}c_i=K$. Since we are only interested in the selections of the actual data plot $i$, the marginal model can be simplified to a beta-binomial model and thus the visual p-value is given as

@@

```{=tex}
\begin{equation} \label{eq:pvalue-beta-binomial}
P(C \geq c_i) = \sum_{x=c_i}^{K}\frac{\Gamma(K + 1)}{\Gamma(x + 1)\Gamma(K - x + 1)}\frac{B(x + \alpha, K - x + (m - 1)\alpha)}{B(\alpha, (m-1)\alpha)},
\end{equation}
```

@@

As discussed in @majumder_validation_2013, individual's skill will affect the number of observers who identify the actual data plot from the lineup. Thus, the power of a visual test depends on the subject-specific abilities. Previously, it was addressed by modelling the probability of a subject $i$ correctly picking the actual data plot from a lineup $l$ using a mixed-effect logistic regression with the subject being treated as a random effect [@majumder_validation_2013]. However, having this probability is insufficient to determine the power of a visual test allowed for multiple selections as it doesn't provide information about the number of selections made by the subject for p-value calculation. Instead, we directly estimated the probability of a lineup being rejected using a logistic regression with the natural logarithm of the effect size as the only regressor. The same model was applied to different subsets of the survey data for making comparison of the power.

@@

Three experiments were conducted to investigate the difference between conventional hypothesis testing and visual inference in the application of linear regression diagnostics. The experiment I has ideal scenario for conventional testing, where the visual test is not expected to outperform the conventional test. Meanwhile, the experiment II is a scenario where the conventional test is an approximate test, in which the visual test may have a chance to match the performance of the conventional test. The experiment III is designed for collecting human responses to lineup with only good residual plots such that the parameter $\alpha$ in Equation \ref{eq:pvalue-beta-binomial} can be estimated. Overall, we planned to collect 7974 evaluations on 1152 uniqued lineups performed by 443 subjects throughout three experiment.

@@

Two types of departures, namely non-linearity and heteroskedasticity, were considered with the corresponding data generating process being designed for experiment I and II.

### 2022-10-01 paper_comparison/paper_comparison/paper_comparison.tex
correct p-value formula
fill in exp overview

\begin{figure}
\includegraphics[width=1\linewidth]{paper_comparison_files/figure-latex/commondepartures-1} \caption{Example fitted vs residual plots: (A) classically good looking residuals, (B) non-linear pattern indicates that the model has not captured a non-linear association, (C) heteroskedasticity indicating that variance around the fitted model is not uniform, and (D) non-normality where the residual distribution is not symmetric around 0. The latter pattern might best be assessed using a univariate plot of the residuals, but patterns B and C need to be assessed using a residual vs fitted plot.}\label{fig:commondepartures}
\end{figure}

Graphical summaries in which residuals are plotted against fitted values
or other functions of the predictor variables that are approximately
orthogonal to residuals are referred to as standard residual plots in
\citet{cook1982residuals}. As shown in Figure
\ref{fig:commondepartures}, the top-left panel is a good residual plot
with residuals evenly distributed at both sides of the horizontal zero
line showing no noticeable patterns. There are various types of
departures from a good residual plot. Two most commonly checked
departures - non-linearity, heterskedasticity and non-normality will be
discussed in this paper.

Non-linearity is a type of model misspecification caused by failing to
include higher order terms of the regressors in the regression equation.
Any non-linear functional form of residuals on fitted values presented
in the residual plot could be considered as an indicative of
non-linearity. An example residual plot containing visual pattern of
non-linearity is given at the top-right of Figure {[}ref here{]}. One
can clearly observe the ``S-shape'' from the residual plot as the cubic
term is not captured by the misspecified model.

Heterskedasticity refers to the presence of nonconst error variance in a
regression model. It is mostly due to the strict but false assumptions
on the variance-covariance matrix of the error term. The usual pattern
of heterskedasticity on a residual plot is the inconsistent spread of
the residuals at different x values. Visually, it sometimes results in
the so-called ``butterfly'' shape as shown in the bottom-left panel of
Figure \ref{fig:commondepartures}, or the ``left-triangle'' and
``right-triganle'' shape where the smallest variance occurs at the edges
of the x-axis.

Compared to non-linearity and heterskedasticity, non-normality is
usually harder to be detected from a residual plot since scatter plot is
not excel in revealing marginal distribution. A favourable graphical
summarise for this task is the quantile-quantile plot. However, for a
consistent comparison in the later part of this paper, residual plot
will be the focus. Besides, it is important to note that not all
regression models assume normality for the error term, but a certain
amount do including the classical normal linear regression model. In the
case that the normality assumption is violated, it is expected to
observe data points that do not centralize around the horizontal zero
line and unevenly distribute at both sides of the zero line. For
example, given a skewed error distribution, fewer data points and more
outliers are on one side of the zero line as shown at the bottom-right
of Figure \ref{fig:commondepartures}.

@@

Example residual plots given in Figure \ref{fig:commondepartures} are
examined by the corresponding model structural test, Breusch-Pagan test
and Shapiro--Wilk test as shown in Table
\ref{tab:example-residual-plot-table}. In the example, both the
Breusch-Pagan test and the Shapiro--Wilk test rejects the null
hypothesis for departures that they do not intend to examine. As
discussed in \citet{cook1982residuals}, most residual-based tests for a
particular type of departure from model assumptions are sensitive to
other types of departures. It is likely the null hypothesis is correctly
rejected but for the wrong reason, which is known as the ``Type III
error''. Additionally, outliers will often incorrectly trigger the
rejection of the null hypothesis despite the residuals are well-behaved
\citep{cook_applied_1999}. This can be largely avoided in diagnostic
plots as experienced analysts can evaluate the acceptability of
assumptions flexibly, even in the presence of outliers.

@@

\caption{\label{tab:example-residual-plot-table}Statistical significance testing for departures from good residuals for plots in Figure \ref{fig:commondepartures}. Shown are the $p$-values calculated for the conventional Model structural, the Breusch-Pagan and the Shapiro–Wilk tests. The good residual plot (A) is judged a good residual plot, as expected, by all tests. The non-linearity (B) is detected by all tests, as might be expected given the extreme structure.}
\centering
\begin{tabular}[t]{llrrr}
\toprule
Plot & Departures & Model structural & Breusch-Pagan & Shapiro–Wilk\\
\midrule
A & None & 0.434 & 0.133 & 0.728\\
B & Non-linearity & \em{0.000} & \em{0.000} & \em{0.039}\\
C & Heteroskedasticity & 0.378 & \em{0.000} & \em{0.000}\\
D & Non-normality & 0.667 & 0.736 & \em{0.000}\\
\bottomrule
\end{tabular}
\end{table}

@@

\begin{equation} \label{eq:pvalue-beta-binomial}
P(C \geq c_i) = \int_{x=c_i}^{K}\frac{\Gamma(K + 1)}{\Gamma(x + 1)\Gamma(K - x + 1)}\frac{B(x + \alpha, K - x + (m - 1)\alpha)}{B(\alpha, (m-1)\alpha)}dx,
\end{equation}

@@

As discussed in \citet{majumder_validation_2013}, individual's skill
will affect the number of observers who identify the actual data plot
from the lineup. Thus, the power of a visual test depends on the
subject-specific abilities. Previously, it was addressed by modelling
the probability of a subject \(i\) correctly picking the actual data
plot from a lineup \(l\) using a mixed-effect logistic regression with
the subject being treated as a random effect
\citep{majumder_validation_2013}. However, knowing this probability is
insufficient to determine the power of a visual test allowed for
multiple selections as it doesn't provide information about the number
of selections made by the subject, and hence, the p-value can't be
computed.

\begin{enumerate}
\def\labelenumi{(\arabic{enumi})}
\item
  Instead, we modelled the probability of a lineup being rejected
  directly using a logistic regression with the natural logarithm of the
  effect size as the only regressor. The same model was applied to
  different subsets of the survey data for making comparison of the
  power.
\item
  Instead, we modelled the plot selection \(c_i\) for the actual data
  plot \(i\).
\end{enumerate}

@@

Three experiments were conducted to investigate the difference between
conventional hypothesis testing and graphical diagnostics in the
application of linear regression diagnostics. The experiment I has ideal
scenario for conventional testing, where the visual test is not expected
to outperform the conventional test. The experiment II is a scenario
where the conventional test is an approximate test, in which the visual
test may have a chance to match the performance of the conventional
test. The experiment III is designed for collecting human responses to
lineup with only good residual plots such that the parameter \(\alpha\)
in Equation \ref{eq:pvalue-beta-binomial} can be estimated. Overall, we
planned to collect 7974 evaluations on 1152 uniqued lineups performed by
443 subjects throughout three experiment.

@@

@@

\includegraphics[width=1\linewidth]{paper_comparison_files/figure-latex/unnamed-chunk-11-1}

\includegraphics[width=1\linewidth]{paper_comparison_files/figure-latex/unnamed-chunk-12-1}

\includegraphics[width=1\linewidth]{paper_comparison_files/figure-latex/unnamed-chunk-13-1}
\includegraphics[width=1\linewidth]{paper_comparison_files/figure-latex/unnamed-chunk-13-2}

\includegraphics[width=1\linewidth]{paper_comparison_files/figure-latex/unnamed-chunk-14-1}
\includegraphics[width=1\linewidth]{paper_comparison_files/figure-latex/unnamed-chunk-14-2}

>>>>

\begin{figure}
\includegraphics[width=1\linewidth]{paper_comparison_files/figure-latex/residual-plot-common-departures-1} \caption{Example fitted vs residual plots: (A) classically good looking residuals, (B) non-linear pattern indicates that the model has not captured a non-linear association, (C) heteroskedasticity indicating that variance around the fitted model is not uniform, and (D) non-normality where the residual distribution is not symmetric around 0. The latter pattern might best be assessed using a univariate plot of the residuals, but patterns B and C need to be assessed using a residual vs fitted plot.}\label{fig:residual-plot-common-departures}
\end{figure}

Graphical summaries in which residuals are plotted against fitted values
or other functions of the predictor variables that are approximately
orthogonal to residuals are referred to as standard residual plots in
\citet{cook1982residuals}. As shown in Figure
\ref{fig:residual-plot-common-departures}, the top-left panel is a good
residual plot with residuals evenly distributed at both sides of the
horizontal zero line showing no noticeable patterns. There are various
types of departures from a good residual plot.

Non-linearity, heterskedasticity and non-normality are perhaps the three
mostly commonly checked departures. Non-linearity is a type of model
misspecification caused by failing to include higher order terms of the
regressors in the regression equation. Any non-linear functional form of
residuals on fitted values presented in the residual plot could be
considered as an indicative of non-linearity. An example residual plot
containing visual pattern of non-linearity is given at the top-right of
Figure {[}ref here{]}. One can clearly observe the ``S-shape'' from the
residual plot as the cubic term is not captured by the misspecified
model. Heterskedasticity refers to the presence of nonconst error
variance in a regression model. It is mostly due to the strict but false
assumptions on the variance-covariance matrix of the error term. The
usual pattern of heterskedasticity on a residual plot is the
inconsistent spread of the residuals at different x values. Visually, it
sometimes results in the so-called ``butterfly'' shape as shown in the
bottom-left panel of Figure \ref{fig:residual-plot-common-departures},
or the ``left-triangle'' and ``right-triganle'' shape where the smallest
variance occurs at the edges of the x-axis. Compared to non-linearity
and heterskedasticity, non-normality is usually harder to be detected
from a residual plot since scatter plot is not excel in revealing
marginal distribution. A favourable graphical summarise for this task is
the quantile-quantile plot. However, for a consistent comparison in the
later part of this paper, residual plot will be the focus. Besides, it
is important to note that not all regression models assume normality for
the error term, but a certain amount do including the classical normal
linear regression model. In the case that the normality assumption is
violated, it is expected to observe data points that do not centralize
around the horizontal zero line and unevenly distribute at both sides of
the zero line. For example, given a skewed error distribution, fewer
data points and more outliers are on one side of the zero line as shown
at the bottom-right of Figure \ref{fig:residual-plot-common-departures}.

@@

Example residual plots given in Figure
\ref{fig:residual-plot-common-departures} are examined by the
corresponding model structural test, Breusch-Pagan test and
Shapiro--Wilk test as shown in Table
\ref{tab:example-residual-plot-table}. In the example, both the
Breusch-Pagan test and the Shapiro--Wilk test rejects the null
hypothesis for departures that they do not intend to examine. As
discussed in \citet{cook1982residuals}, most residual-based tests for a
particular type of departure from model assumptions are sensitive to
other types of departures. It is likely the null hypothesis is correctly
rejected but for the wrong reason, which is known as the ``Type III
error''. Additionally, outliers will often incorrectly trigger the
rejection of the null hypothesis despite the residuals are well-behaved
\citep{cook_applied_1999}. This can be largely avoided in diagnostic
plots as experienced analysts can evaluate the acceptability of
assumptions flexibly, even in the presence of outliers.

@@

\caption{\label{tab:example-residual-plot-table}Statistical significance testing for departures from good residuals for plots in Figure \ref{fig:residual-plot-common-departures}. Shown are the $p$-values calculated for the conventional Model structural, the Breusch-Pagan and the Shapiro–Wilk tests. The good residual plot (A) is judged a good residual plot, as expected, by all tests. The non-linearity (B) is detected by all tests, as might be expected given the extreme structure.}
\centering
\begin{tabular}[t]{llrrr}
\toprule
Plot & Departures & Model structural & Breusch-Pagan & Shapiro–Wilk\\
\midrule
A & None & 0.434 & 0.133 & 0.728\\
B & Non-linearity & \em{0.000} & \em{0.000} & \em{0.039}\\
C & Heteroskedasticity & 0.378 & \em{0.000} & \em{0.000}\\
D & Non-normality & 0.667 & 0.736 & \em{0.000}\\
\bottomrule
\end{tabular}
\end{table}

@@

\begin{equation} \label{eq:pvalue-beta-binomial}
P(C \geq c_i) = \sum_{x=c_i}^{K}\frac{\Gamma(K + 1)}{\Gamma(x + 1)\Gamma(K - x + 1)}\frac{B(x + \alpha, K - x + (m - 1)\alpha)}{B(\alpha, (m-1)\alpha)},
\end{equation}

@@

As discussed in \citet{majumder_validation_2013}, individual's skill
will affect the number of observers who identify the actual data plot
from the lineup. Thus, the power of a visual test depends on the
subject-specific abilities. Previously, it was addressed by modelling
the probability of a subject \(i\) correctly picking the actual data
plot from a lineup \(l\) using a mixed-effect logistic regression with
the subject being treated as a random effect
\citep{majumder_validation_2013}. However, having this probability is
insufficient to determine the power of a visual test allowed for
multiple selections as it doesn't provide information about the number
of selections made by the subject for p-value calculation. Instead, we
directly estimated the probability of a lineup being rejected using a
logistic regression with the natural logarithm of the effect size as the
only regressor. The same model was applied to different subsets of the
survey data for making comparison of the power.

@@

Three experiments were conducted to investigate the difference between
conventional hypothesis testing and visual inference in the application
of linear regression diagnostics. The experiment I has ideal scenario
for conventional testing, where the visual test is not expected to
outperform the conventional test. Meanwhile, the experiment II is a
scenario where the conventional test is an approximate test, in which
the visual test may have a chance to match the performance of the
conventional test. The experiment III is designed for collecting human
responses to lineup with only good residual plots such that the
parameter \(\alpha\) in Equation \ref{eq:pvalue-beta-binomial} can be
estimated. Overall, we planned to collect 7974 evaluations on 1152
uniqued lineups performed by 443 subjects throughout three experiment.

@@

\includegraphics[width=1\linewidth]{paper_comparison_files/figure-latex/unnamed-chunk-6-1}

\includegraphics[width=1\linewidth]{paper_comparison_files/figure-latex/unnamed-chunk-7-1}

@@

\includegraphics[width=1\linewidth]{paper_comparison_files/figure-latex/unnamed-chunk-11-1}
\includegraphics[width=1\linewidth]{paper_comparison_files/figure-latex/unnamed-chunk-11-2}

\includegraphics[width=1\linewidth]{paper_comparison_files/figure-latex/unnamed-chunk-12-1}
\includegraphics[width=1\linewidth]{paper_comparison_files/figure-latex/unnamed-chunk-12-2}
